---
title: "Regime Identification Experiments"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bnlearn)
library(gRain)
library(Rgraphviz)
library(graph)
library(grid)
library(snow)
library(tidyverse)
library(lubridate)
```

## Experimenting with k
While allowing number of allowed transition to be greater than 3, for e.g. 4,5,6 has not yielded more  unique non zero deltas representing the unique positions than 3.


## Experiments with blacklisting arcs 


Experiments with blacklisting arcs, for a model with 23 variables (11 original + 12 ), the model does not seem to work well. 

## Structure learning Chicago Bulls 
Regime location identified as 1283,	2106,	2776
1189	2022	2773

## Predictions for the last regimes
R1 "1999-02-09"
> gamelog_stat_chicago$Date[1283]
[1] "1999-02-11"
> gamelog_stat_chicago$Date[2105]
[1] "2009-01-12"
> gamelog_stat_chicago$Date[2106]
[1] "2009-01-14"
> gamelog_stat_chicago$Date[2775]
[1] "2017-03-15"
> gamelog_stat_chicago$Date[2776]
[1] "2017-03-17"










```{r}

regime_list<-list(1:1282,1283:2105,2106:2774,2775:3090)

#dag4=model2network("[HomeAway][DefFT_d_FGA][OffeFGper][OffTOVper][OffORBper][OffFT_d_FGA][DefeFGper][DefDR#Bper][DefTOVper|DefFT_d_FGA][WL|OffeFGper:OffTOVper:OffORBper:OffFT_d_FGA:DefeFGper:DefFT_d_FGA:DefTOVper:#DefDRBper][PlayOff|WL]")


gamelog_stat_chicago=read.csv('~/Desktop/GBN-Regime-in-Basketball/data/PreProcessed_Chicago_Gamelog.csv')

gamelog_discrete_chicago<-discretize(gamelog_stat_chicago[,-c(1:15,24:25)],method='quantile',breaks = 5)


#gamelog_discrete_chicago$Opp<-factor(gamelog_stat_chicago$Opp)
gamelog_discrete_chicago$WL<-factor(gamelog_stat_chicago$WL)
gamelog_discrete_chicago$PlayOff<-factor(gamelog_stat_chicago$PlayOff)
gamelog_discrete_chicago$HomeAway<-factor(gamelog_stat_chicago$HomeAway)



regime_data=gamelog_discrete_chicago[regime_list[[4]],]

set.seed(1728)
train_id=sample(1:dim(regime_data)[1],floor(0.80*dim(regime_data)[1]))

regime_data_train=regime_data[train_id,]
regime_data_test=regime_data[-train_id,]


bn<-hc(regime_data_train,
        score = 'bde',
        restart = 1000,
        maxp=8)
cat('\nBDe score ',bnlearn::score(bn,regime_data_train))
graphviz.plot(bn)



#computing accuracy of learned BN for training data



fitted_expertBN<-bn.fit(bn,data=as.data.frame(regime_data_train))
fitted_grain<-as.grain(fitted_expertBN)


train_predictions<-c()


for (i in 1:dim(regime_data_train)[1]) {

    bn_net<-setEvidence(compile(fitted_grain),nodes = colnames(regime_data_train)[-9],
                states = c(as.character(regime_data_train$OffeFGper[i]),
                           as.character(regime_data_train$OffTOVper[i]),
                           as.character(regime_data_train$OffORBper[i]),
                           as.character(regime_data_train$OffFT_d_FGA[i]),
                           as.character(regime_data_train$DefeFGper[i]),
                           as.character(regime_data_train$DefTOVper[i]),
                           as.character(regime_data_train$DefDRBper[i]),
                           as.character(regime_data_train$DefFT_d_FGA[i]),
                           as.character(regime_data_train$PlayOff[i]),
                           as.character(regime_data_train$HomeAway[i])
                           ))

    x<-querygrain(bn_net,'WL')
    train_predictions=rbind(train_predictions,x$WL)
    
}

pred<-apply(train_predictions,MARGIN = 1,FUN = which.max)
predicted_outcome<-factor(ifelse(pred==1,'L','W'))

tb<-table(predicted_outcome,regime_data_train$WL)
cat('\n train accuracy',sum(diag(tb))/sum(tb))

#################################
#computing accuracy of learned BN for test data
test_predictions<-c()



for (i in 1:dim(regime_data_test)[1]) {

    bn_net<-setEvidence(compile(fitted_grain),nodes = colnames(regime_data_test)[-9],
                states = c(as.character(regime_data_test$OffeFGper[i]),
                           as.character(regime_data_test$OffTOVper[i]),
                           as.character(regime_data_test$OffORBper[i]),
                           as.character(regime_data_test$OffFT_d_FGA[i]),
                           as.character(regime_data_test$DefeFGper[i]),
                           as.character(regime_data_test$DefTOVper[i]),
                           as.character(regime_data_test$DefDRBper[i]),
                           as.character(regime_data_test$DefFT_d_FGA[i]),
                           as.character(regime_data_test$PlayOff[i]),
                           as.character(regime_data_test$HomeAway[i])
                           ))

    x<-querygrain(bn_net,'WL')
    test_predictions=rbind(test_predictions,x$WL)
    
}

pred<-apply(test_predictions,MARGIN = 1,FUN = which.max)
predicted_outcome<-factor(ifelse(pred==1,'L','W'))

tb<-table(predicted_outcome,regime_data_test$WL)
cat('\ntest accuracy',sum(diag(tb))/sum(tb))

```




```{r}



#dag_main=model2network("[OffORBper][DefTOVper|OffORBper][HomeAway|OffORBper][OffFT_d_FGA|OffORBper][OffeFGper|DefTOVper]#[DefFT_d_FGA|OffFT_d_FGA:DefTOVper:HomeAway][DefDRBper|OffFT_d_FGA:OffORBper:DefTOVper:HomeAway][OffTOVper|OffFT_d_FGA:O#ffeFGper:DefTOVper:HomeAway][DefeFGper|DefDRBper:OffTOVper:HomeAway:OffeFGper:DefTOVper][WL|OffFT_d_FGA:DefFT_d_FGA:DefD#RBper:OffTOVper:OffeFGper:DefeFGper:DefTOVper:OffORBper][PlayOff|WL]")


regime_list<-list(1:1282,1283:2105,2106:2774,2775:3090)

#dag4=model2network("[HomeAway][DefFT_d_FGA][OffeFGper][OffTOVper][OffORBper][OffFT_d_FGA][DefeFGper][DefDR#Bper][DefTOVper|DefFT_d_FGA][WL|OffeFGper:OffTOVper:OffORBper:OffFT_d_FGA:DefeFGper:DefFT_d_FGA:DefTOVper:#DefDRBper][PlayOff|WL]")


gamelog_stat_chicago=read_csv('~/Desktop/GBN-Regime-in-Basketball/data/PreProcessed_Chicago_Gamelog.csv')

gamelog_discrete_chicago<-discretize(gamelog_stat_chicago[,-c(1:15,24:25)],method='quantile',breaks = 5)


#gamelog_discrete_chicago$Opp<-factor(gamelog_stat_chicago$Opp)
gamelog_discrete_chicago$WL<-factor(gamelog_stat_chicago$WL)
gamelog_discrete_chicago$PlayOff<-factor(gamelog_stat_chicago$PlayOff)
gamelog_discrete_chicago$HomeAway<-factor(gamelog_stat_chicago$HomeAway)



regime_data=gamelog_discrete_chicago[regime_list[[4]],]

set.seed(1728)
train_id=sample(1:dim(regime_data)[1],floor(0.80*dim(regime_data)[1]))

regime_data_train=regime_data[train_id,]
regime_data_test=regime_data[-train_id,]


bn<-hc(gamelog_discrete_chicago,
        score = 'bde',
        restart = 1000,
        maxp=8)
cat('\nBDe score',bnlearn::score(bn,regime_data_train))
graphviz.plot(bn)


##fitting the model and setting up for evidence propogation using gRain package


fitted_expertBN<-bn.fit(bn,data=as.data.frame(gamelog_discrete_chicago))
fitted_grain<-as.grain(fitted_expertBN)


#computing training  accuracy of BN using entire dataset
train_predictions<-c()
for (i in 1:dim(regime_data_train)[1]) {

    bn_net<-setEvidence(compile(fitted_grain),nodes = colnames(regime_data_train)[-9],
                states = c(as.character(regime_data_train$OffeFGper[i]),
                           as.character(regime_data_train$OffTOVper[i]),
                           as.character(regime_data_train$OffORBper[i]),
                           as.character(regime_data_train$OffFT_d_FGA[i]),
                           as.character(regime_data_train$DefeFGper[i]),
                           as.character(regime_data_train$DefTOVper[i]),
                           as.character(regime_data_train$DefDRBper[i]),
                           as.character(regime_data_train$DefFT_d_FGA[i]),
                           as.character(regime_data_train$PlayOff[i]),
                           as.character(regime_data_train$HomeAway[i])
                           ))

    x<-querygrain(bn_net,'WL')
    train_predictions=rbind(train_predictions,x$WL)
    
}

pred<-apply(train_predictions,MARGIN = 1,FUN = which.max)
predicted_outcome<-factor(ifelse(pred==1,'L','W'))

tb<-table(predicted_outcome,regime_data_train$WL)
cat('train accuracy',sum(diag(tb))/sum(tb))

#################################
#computing accuracy of learned BN for test data
test_predictions<-c()



for (i in 1:dim(regime_data_test)[1]) {

    bn_net<-setEvidence(compile(fitted_grain),nodes = colnames(regime_data_test)[-9],
                states = c(as.character(regime_data_test$OffeFGper[i]),
                           as.character(regime_data_test$OffTOVper[i]),
                           as.character(regime_data_test$OffORBper[i]),
                           as.character(regime_data_test$OffFT_d_FGA[i]),
                           as.character(regime_data_test$DefeFGper[i]),
                           as.character(regime_data_test$DefTOVper[i]),
                           as.character(regime_data_test$DefDRBper[i]),
                           as.character(regime_data_test$DefFT_d_FGA[i]),
                           as.character(regime_data_test$PlayOff[i]),
                           as.character(regime_data_test$HomeAway[i])
                           ))

    x<-querygrain(bn_net,'WL')
    test_predictions=rbind(test_predictions,x$WL)
    
}

pred<-apply(test_predictions,MARGIN = 1,FUN = which.max)
predicted_outcome<-factor(ifelse(pred==1,'L','W'))

tb<-table(predicted_outcome,regime_data_test$WL)
cat('\ntest accuracy',sum(diag(tb))/sum(tb))






```

